\myfirstcvitem{Undergraduate Courses}{%
\begin{itemize}
\item[]
Operating Systems, University of Salzburg, Winter 2019.
Systems Engineering, University of Salzburg, Winter 2019.
Compiler Construction, University of Salzburg, Summer 2019.
Operating Systems, University of Salzburg, Winter 2018.
Systems Engineering, University of Salzburg, Winter 2018.
Compiler Construction, University of Salzburg, Summer 2018.
Operating Systems, University of Salzburg, Winter 2017.
Systems Engineering, University of Salzburg, Winter 2017.
Compiler Construction, University of Salzburg, Summer 2017.
\myteachurl{CC-Summer-2016}{Compiler Construction}, University of Salzburg, Summer 2016.
\myteachurl{IOS-Winter-2015}{Operating Systems}, University of Salzburg, Winter 2015.
\myteachurl{SE-Winter-2015}{Systems Engineering}, University of Salzburg, Winter 2015.
\myteachurl{CC-Summer-2015}{Compiler Construction}, University of Salzburg, Summer 2015.
\myteachurl{IOS-Winter-2014}{Operating Systems}, University of Salzburg, Winter 2014.
\myteachurl{SE-Winter-2014}{Systems Engineering}, University of Salzburg, Winter 2014.
\myteachurl{CC-Summer-2014}{Compiler Construction}, University of Salzburg, Summer 2014.
\myteachurl{IOS-Winter-2013}{Operating Systems}, University of Salzburg, Winter 2013.
\myteachurl{CC-Summer-2013}{Compiler Construction}, University of Salzburg, Summer 2013.
\myteachurl{CC-Summer-2012}{Compiler Construction}, University of Salzburg, Summer 2012.
\myteachurl{CC-Summer-2011}{Compiler Construction}, University of Salzburg, Summer 2011.
\myteachurl{CC-Summer-2010}{Compiler Construction}, University of Salzburg, Summer 2010.
\myteachurl{CC-Summer-2009}{Compiler Construction}, University of Salzburg, Summer 2009.
\end{itemize}
}

\myfirstcvitem{Graduate Courses}{%
\begin{itemize}
\item[]
Advanced Operating Systems, University of Salzburg, Winter 2019.
Advanced Operating Systems, University of Salzburg, Winter 2018.
Advanced Operating Systems, University of Salzburg, Winter 2017.
\myteachurl{AOS-Winter-2015}{Advanced Operating Systems}, University of Salzburg, Winter 2015;
\myteachurl{AOS-Winter-2014}{Advanced Operating Systems}, University of Salzburg, Winter 2014;
\myteachurl{CE290I-Fall-2014}{Control and Information Management}, University of California, Berkeley, Fall 2014;
\myteachurl{AOS-Winter-2013}{Advanced Operating Systems}, University of Salzburg, Winter 2013;
\myteachurl{AOS-Winter-2011}{Advanced Operating Systems}, University of Salzburg, Winter 2011;
\myteachurl{ESE-Winter-2011}{Embedded Software Engineering}, University of Salzburg, Winter 2011;
\myteachurl{ESE-Winter-2010}{Embedded Software Engineering}, University of Salzburg, Winter 2010;
\myteachurl{ESE-Winter-2009}{Embedded Software Engineering}, University of Salzburg, Winter 2009;
\myteachurl{OS-Winter-2009}{Advanced Operating Systems}, University of Salzburg, Winter 2009;
\myteachurl{CC-Summer-2008}{Compiler Construction}, University of Salzburg, Summer 2008;
\myteachurl{OS-Winter-2007}{Operating Systems}, University of Salzburg, Winter 2007;
\myteachurl{CC-Summer-2007}{Compiler Construction}, University of Salzburg, Summer 2007;
\myteachurl{ESE-Winter-2006}{Embedded Software Engineering}, University of Salzburg, Winter 2006;
\myteachurl{OS-Winter-2006}{Operating Systems}, University of Salzburg, Winter 2006;
\myteachurl{CC-Summer-2006}{Compiler Construction}, University of Salzburg, Summer 2006;
\myteachurl{TCS-Summer-2006}{Theory of Computational Systems}, University of Salzburg, Summer 2006;
\myteachurl{ESE-Winter-2005}{Embedded Software Engineering}, University of Salzburg, Winter 2005;
\myteachurl{OS-Winter-2005}{Operating Systems}, University of Salzburg, Winter 2005;
\myteachurl{CC-Summer-2005}{Compiler Construction}, University of Salzburg, Summer 2005;
\myteachurl{TCS-Summer-2005}{Theory of Computational Systems}, University of Salzburg, Summer 2005;
\myteachurl{CSE-Winter-2004}{Computational Systems Engineering}, University of Salzburg, Winter 2004;
\myteachurl{ESE-Winter-2004}{Embedded Software Engineering}, University of Salzburg, Winter 2004;
\myteachurl{EECS290O-Spring-2002}{Embedded Software Engineering}, UC Berkeley (EECS290O), Spring 2002;
\myteachurl{EECS290O-Spring-2001}{Embedded Software Engineering}, UC Berkeley (EECS290O), Spring 2001.
\end{itemize}
}

\mycvitem{Graduate Seminars}{%
\begin{itemize}
\item[]
\myteachurl{CMM-Summer-2015}{Concurrency and Memory Management Seminar}, University of Salzburg, Summer 2015;
\myteachurl{CMM-Summer-2014}{Concurrency and Memory Management Seminar}, University of Salzburg, Summer 2014;
\myteachurl{CMM-Summer-2013}{Concurrency and Memory Management Seminar}, University of Salzburg, Summer 2013;
\myteachurl{CMM-Summer-2012}{Concurrency and Memory Management Seminar}, University of Salzburg, Summer 2012;
\myteachurl{CMM-Winter-2010}{Concurrency and Memory Management Seminar}, University of Salzburg, Winter 2010;
\myteachurl{SWS-Summer-2010}{Software Systems Seminar}, University of Salzburg, Summer 2010;
\myteachurl{SWS-Summer-2009}{Software Systems Seminar}, University of Salzburg, Summer 2009;
\myteachurl{SWS-Summer-2008}{Software Systems Seminar}, University of Salzburg, Summer 2008;
\myteachurl{COPS-Winter-2007}{Compositionality Seminar}, University of Salzburg, Winter 2007;
\myteachurl{SWS-Summer-2007}{Software Systems Seminar}, University of Salzburg, Summer 2007;
\myteachurl{CS-Summer-2004}{Computational Systems Seminar}, University of Salzburg, Summer 2004.
\end{itemize}
}