\begin{refsection}

\nocite{PaCT13}
\nocite{PoS13}
\nocite{ISMM13}
\nocite{SysCon13}
\nocite{ICCPS13}
\nocite{POPL13}
\nocite{EUC12}
\nocite{RACES12}
\nocite{ICA3PP12}
\nocite{DAC12}
\nocite{DATE12}
\nocite{ICONS12}
\nocite{AASGNC12}
\nocite{ACSD11}
\nocite{PODC11}
\nocite{ISMM11}
\nocite{FACS10}
\nocite{EMSOFT10}
\nocite{HotCloud10}
\nocite{RTAS10}
\nocite{RTSS09}
\nocite{RePP09}
\nocite{JTRES09}
\nocite{SIES09}
\nocite{RTAS09b}
\nocite{IIES09}
\nocite{WISH09}
\nocite{AIAAGNC08}
\nocite{USENIX08}
\nocite{APRES08}
\nocite{DATE08}
\nocite{EMSOFT07b}
\nocite{APGES07}
\nocite{LCTES07}
\nocite{EMSOFT06}
\nocite{VEE05}
\nocite{LCTES05}
\nocite{MontereyWorkshop04}
\nocite{EMSOFT04}
\nocite{HSCC04}
\nocite{EMSOFT03}
\nocite{PLDI02}
\nocite{EMSOFT02a}
\nocite{EMSOFT02b}
\nocite{EMSOFT01a}
\nocite{LCTES01}
\nocite{DASC01}
\nocite{LICS99}
\nocite{AIML98}
\nocite{RTA98}
\nocite{CADE97}
\nocite{CADE96}

\mybibitem{Conference and Workshop Papers}
\printbibliography[heading=none]

\end{refsection}

\begin{refsection}

\nocite{STTT13}
\nocite{SCP12}
\nocite{TECS09}
\nocite{OSR08}
\nocite{TOPLAS07}
\nocite{IEEE03}
\nocite{CSM03}

\mybibitem{Journal Papers}
\printbibliography[heading=none]

\end{refsection}

\begin{refsection}

\nocite{CF13}
\nocite{EMSOFT05}
\nocite{EMSOFT02c}

\mybibitem{Invited Papers}
\printbibliography[heading=none]

\end{refsection}

\begin{refsection}

\nocite{EuroSys11}
\nocite{LCTES09}
\nocite{EMSOFT07a}
\nocite{EMSOFT01}

\mybibitem{Proceedings}
\printbibliography[heading=none]

\end{refsection}

\begin{refsection}

\nocite{ARTS12}
\nocite{HRTES07}
\nocite{SEC03}

\mybibitem{Book Chapters}
\printbibliography[heading=none]

\end{refsection}

\begin{refsection}

\nocite{ICSE01}
\nocite{JAR98}

\mybibitem{System Papers}
\printbibliography[heading=none]

\end{refsection}

\begin{refsection}

\nocite{EuroSys10}
\nocite{RTAS09a}

\mybibitem{Posters}
\printbibliography[heading=none]

\end{refsection}

\begin{refsection}

\nocite{SBG12b}
\nocite{SBG12a}
\nocite{SBG11b}
\nocite{SBG11a}
\nocite{SBG10e}
\nocite{SBG10d}
\nocite{SBG10c}
\nocite{SBG10b}
\nocite{SBG10a}
\nocite{SBG09b}
\nocite{SBG09a}
\nocite{SBG08}
\nocite{SBG07}
\nocite{KTH06}
\nocite{UCB06}
\nocite{SBG05}
\nocite{SBG04}
\nocite{UCB03a}
\nocite{UCB03b}
\nocite{UCB01}
\nocite{UCB00}
\nocite{MPI98}
\nocite{MPI93}

\mybibitem{Technical Reports}
\printbibliography[heading=none]

\end{refsection}

\begin{refsection}

\nocite{Meyer99}
\nocite{Meyer96}

\mybibitem{Theses}
\printbibliography[heading=none]

\end{refsection}

\mycvitem{Software}{%
\begin{enumerate}
\item The Scal Project: High-Performance, Multicore-Scalable Data Structures,
with Andreas Haas, Thomas A. Henzinger, Michael Lippautz, Hannes Payer, Ali Sezgin, and Ana Sokolova.
Web: \url{http://scal.cs.uni-salzburg.at}

\item The Tiptoe Project: A Compositional Real-Time Operating System,
with Silviu Craciunas, Hannes Payer, Harald R{\"o}ck, Ana Sokolova, and Horst Stadler.
Web: \url{http://tiptoe.cs.uni-salzburg.at}

\item The Jarol Project: A Java Infrastructure for Control Systems,
with Bernhard Kast, Eduardo Marques, and Rainer Trummer.
Web: \url{http://jarol.cs.uni-salzburg.at}

\item The JAviator Project: Quadrotor UAV Software Entirely Written in Java,
with Joshua Auerbach, David Bacon, Harald R{\"o}ck, and Rainer Trummer.
Web: \url{http://javiator.cs.uni-salzburg.at}

\item The TAP Project: Concurrent Programming with Threading by Appointment,
with Silviu Craciunas and Harald R{\"o}ck.  Web: \url{http://tap.cs.uni-salzburg.at}

\item The HTL Project: Compositional Real-Time Programming in a Hierarchical Timing Language,
with Arkadeb Ghosal, Thomas A. Henzinger, Daniel Iercan, and Alberto L. Sangiovanni-Vincentelli.
Web: \url{http://htl.cs.uni-salzburg.at}

\item Giotto: An Embedded Programming Language, Compiler, and Runtime System for Distributed Control Systems,
with Arkadeb Ghosal, Thomas A. Henzinger, Slobodan Matic, and Marco A.A. Sanvido.
Web: \url{http://embedded.eecs.berkeley.edu/giotto}

\item jMocha: A Model Checking Tool that Exploits Design Structure,
with Rajeev Alur, Luca de Alfaro, Radu Grosu, Thomas A. Henzinger,
Minsu Kang, Rupak Majumdar, Freddy Mang, and Bow-Yaw Wang.  Web:
\url{http://embedded.eecs.berkeley.edu/research/mocha}

\item SPASS v0.77: An Automated Theorem Prover for First-Order Logic with Equality,
with Christoph Weidenbach, Christian Cohrs, Thorsten Engel, and Enno
Keen.  Web: \url{http://spass.mpi-sb.mpg.de}

\item PURR: Parallel Unit Resulting Resolution, a concurrent first-order theorem prover
with advanced indexing operations, see Master's Thesis.

\item ACID: A Collection of Indexing Data Structures, implemented in C and Prolog,
with Peter Graf.
\end{enumerate}
}

\mycvitem{Hardware}{%
\begin{enumerate}
\item The JAviator: A Quadrotor Helicopter and Software Laboratory for Time-Portable Java Programming,
with Rainer Trummer.  Web: \url{http://javiator.cs.uni-salzburg.at}
\end{enumerate}
}
