\myfirstcvitem{Invited Talks}{%
\begin{enumerate}
\item \emph{From Logical Execution Time to Principled Systems Engineering}, Dagstuhl Seminar on the Logical Execution Time Paradigm, Schloss Dagstuhl, Wadern, Germany.
\mytalkurl{Dagstuhl18-LET-Selfie}.

\item \emph{You can program what you want but you cannot compute what you want}, Edward A.~Lee Festschrift Symposium, UC Berkeley, Berkeley, California, October 2017.
\mytalkurl{Festschrift17-Selfie}.

\item \emph{Design versus Performance: From Giotto via the Embedded Machine to Selfie}, ACM SIGPLAN/SIGBED Conference on Languages, Compilers, and Tools for Embedded Systems (LCTES), Barcelona, Spain, June 2017.
\mytalkurl{LCTES17-Selfie}.

\item \emph{Scalloc: From Relaxed Concurrent Data Structures to the Fastest Multicore-Scalable Memory Allocator},
International Conference on Networked Systems (NETYS), Agadir, Morocco, May 2015.
\mytalkurl{NETYS15-Scalloc}.

\item \emph{Concurrent Data Structures: Fast but Relaxed versus Strict but Slow Semantics},
International Workshop on the Chemistry of Concurrent and Distributed Programming (CCDP), Agadir, Morocco, May 2015.
\mytalkurl{CCDP15-ConcurrentDataStructures}.

\item \emph{Distributed Queues in Shared Memory---Multicore Performance and Scalability through Quantitative Relaxation},
ACM Computing Frontiers, Ischia, Italy, May 2013.
\mytalkurl{CF13-DQ}.

\item \emph{Inexact Software Is the Solution},
CASA Workshop, Tampere, Finland, October 2012.
\mytalkurl{CASA12-ISIS}.

\item \emph{Incorrect Systems: It's not the Problem, It's the Solution},
EC2 Workshop, Berkeley, California, July 2012.
\mytalkurl{EC212-Incorrectness}.

\item \emph{Incorrect Systems: It's not the Problem, It's the Solution},
Austrian Computer Science Day, University of Vienna, Austria, June 2012.
\mytalkurl{ACSD12-Incorrectness}.

\item \emph{Virtualizing Time, Space, and Power for Cyber-Physical Cloud Computing},
ARTIST Workshop on Rigorous Embedded Design, Salzburg, Austria, April 2011.
\mytalkurl{RED11-CPCC}.

\item \emph{Short-term Memory for Self-collecting Mutators: Towards Time- and Space-predictable Virtualization},
Computer Science Symposium, IST Austria, Klosterneuburg, Austria, May 2010.
\mytalkurl{ISTA10-STMVirtualization}.

\item \emph{Tiptoe: A Compositional Real-Time Operating System (Memory Management)},
ARTIST Workshop on Foundations and Applications of Component-Based Design, Salzburg, Austria, September 2007.
\mytalkurl{WFCD07-Tiptoe}.

\item \emph{Trends and Challenges in Embedded Systems Research},
{\"O}sterreichische Forschungsf{\"o}rderungsgesellschaft (FFG), Vienna, Austria, May, 2007.
\mytalkurl{FIT-IT07-TrendsChallenges}.

\item \emph{Shaping Process Semantics (and the JAviator: A Flying MoCC Laboratory)},
ARTIST Workshop on Models of Computation and Communication, Z{\"u}rich, Switzerland, November 2006.
\mytalkurl{ARTIST06-ProcessShaping-JAviator}

\item \emph{Shaping Process Semantics},
Monterey Workshop on Composition of Embedded Systems: Scientific and Industrial Issues,
Paris, France, October 2006.
\mytalkurl{Monterey06-ProcessShaping}.

\item \emph{Threading by Appointment},
Monterey Workshop on Software Engineering Tools: Compatibility and Integration, Vienna, Austria, October 2004.
\mytalkurl{Monterey04-TAP}.

\item \emph{Embedded Systems Frontiers},
Bundesministerium f{\"u}r Verkehr, Innovation und Technologie, Vienna, Austria, July 2003.
\mytalkurl{BMVIT03-EmbeddedSystemsFrontier}.

\item \emph{Principles of Real-Time Programming},
Second International Workshop on Embedded Software (EMSOFT), Grenoble, France, October 2002.
\mytalkurl{EMSOFT02-PrinciplesRTProgramming}.
\end{enumerate}
}

\mycvitem{Panels}{%
\begin{enumerate}
\item \emph{Looking at Past Data to Improve the Future}, Embedded Systems Week, Montreal, Canada, October 2013.
\item \emph{Vehicular Wireless Networks: What should the future hold?},
International Symposium on Wireless Vehicular Communications (WiVeC), San Francisco, California, September 2011.
\item \emph{Collaboration and Virtualization in Cyber-Physical Systems},
CPS Forum, Cyber-Physical Systems Week, San Francisco, California, April 2009.
\mytalkurl{CPS-Forum-2009}
\end{enumerate}
}

\mycvitem{Colloquia}{%
\begin{enumerate}
\item \emph{Time-Portable Programming the JAviator in Tiptoe OS},
Department of Computer Science and Engineering, UC Riverside, California, October 2008.
\mytalkurl{UCR08-JAviator}.

\item \emph{Tiptoe: A Compositional Real-Time Operating System (Memory Management)},
Center for Embedded Computer Systems, UC Irvine, California, March 2008.
\mytalkurl{UCI08-Tiptoe}.
\end{enumerate}
}

\mycvitem{Schools}{%
\begin{enumerate}
\item \emph{Scal, Scalloc, and Selfie: Fast Multicore-Scalable Concurrent Data Structures and Memory Management, and Educational Self-referential Systems Software},
UPMARC Summer School on Multicore Computing, Uppsala, Sweden, June 2016.
\mytalkurl{UPMARC16-Scal-Scalloc-Selfie}.

\item \emph{Design of Concurrent and Distributed Data Structures},
International Spring School on Distributed Systems (METIS), Agadir, Morocco, May 2015.
\mytalkurl{METIS15-ConcurrentDataStructures}.

\item \emph{Virtualizing Time, Space, and Power for Cyber-Physical Cloud Computing},
Georgia Tech Summer School on Cyber-Physical Systems, Atlanta, Georgia, USA, June, 2011.
\mytalkurl{GATECH11-CPCC}.

\item \emph{Explicit, Dynamic Memory Management with Temporal and Spatial Guarantees},
ARTIST Summer School on Embedded Systems Design, Buenos Aires, Argentina, August 2009.
\mytalkurl{ARTIST09-Summer-School-Buenos-Aires}.

\item \emph{Explicit, Dynamic Memory Management with Temporal and Spatial Guarantees},
ARTIST Summer School on Embedded Systems Design, Beijing, China, July 2009.
\mytalkurl{ARTIST09-Summer-School-Beijing}.

\item \emph{Designing a Compositional Real-Time Operating System},
ARTIST Summer School on Embedded Systems Design, Shanghai, China, July 2008.
\mytalkurl{ARTIST08-Summer-School-Shanghai}.

\item \emph{From Control Models to Real-Time Code Using Giotto},
Summer School on Embedded Systems (EmSys), Salzburg, Austria, June 2003.
\mytalkurl{EmSys03-ControlModels}.

\item \emph{Principles of Real-Time Programming},
Summer School on Embedded Systems (EmSys), Salzburg, Austria, June 2003.
\mytalkurl{EmSys03-PrinciplesRTProgramming}.
\end{enumerate}
}

\mycvitem{Tutorial}{%
\begin{enumerate}
\item \emph{The Logical Execution Time Paradigm}, Tutorials on Time-Predictable and Composable Architectures for Dependable Embedded Systems, ESWEEK, Taipei, Taiwan, October 2011.
\mytalkurl{ESWEEK11-LET}.
\end{enumerate}
}

\mycvitem{Conferences and Seminars}{%
\begin{enumerate}
\item \emph{Self-Referential Compilation, Emulation, Virtualization, and Symbolic Execution with Selfie}, Google, Munich, Germany, 2018.
\mytalkurl{Google18-Selfie}.

\item \emph{Selfie and the Basics}, University of Freiburg, Germany, 2017.
\mytalkurl{Freiburg17-Selfie}.

\item \emph{Selfie and the Basics}, Onward!, Vancouver, British Columbia, 2017.
\mytalkurl{Onward17-Selfie}.

\item \emph{Selfie: A Sandbox for Principled Systems Engineering}, ARM Research Summit, Cambridge, UK, 2017.
\mytalkurl{ARMSummit17-Selfie}.

\item \emph{Scal, Scalloc, and Selfie}, University of Cambridge, Cambridge, UK, 2017.
\mytalkurl{Cambridge17-Scal-Scalloc-Selfie}.

\item \emph{Selfie: Sandboxed Concurrency},
Research Seminar on Open Problems in Concurrency Theory (OPCT), IST Austria, Klosterneuburg, Austria, June 2017.
\mytalkurl{OPCT17-Selfie}.

\item \emph{Selfie: What is the Difference between Emulation and Virtualization?},
ETH Zurich, Zurich, Switzerland, March 2017.
\mytalkurl{ETH17-Selfie-Vipster}.

\item \emph{Teaching Computer Science Through Self-Referentiality},
Helmut Veith Memorial Workshop, Obergurgl, Austria, February 2017.
\mytalkurl{HVM17-Selfie}.

\item \emph{Teaching Computer Science Through Self-Referentiality},
Hong Kong University of Science and Technology, Hong Kong, China, January 2017.
\mytalkurl{HKUST17-Selfie}.

\item \emph{Scal, Scalloc, and Selfie},
University of Melbourne, Melbourne, Australia, December 2016.
\mytalkurl{MELBOURNE16-Scal-Scalloc-Selfie}.

\item \emph{Scal, Scalloc, and Selfie},
Australien National University and DATA61, Canberra, Australia, December 2016.
\mytalkurl{ANU16-Scal-Scalloc-Selfie}.

\item \emph{Scal, Scalloc, and Selfie},
University of New South Wales and DATA61, Sydney, Australia, November 2016.
\mytalkurl{UNSW16-Scal-Scalloc-Selfie}.

\item \emph{Scal, Scalloc, and Selfie},
IST Austria, Klosterneuburg, Austria, September 2016.
\mytalkurl{ISTA16-Scal-Scalloc-Selfie}.

\item \emph{Scal, Scalloc, and Selfie},
Northeastern University, Boston, Massachusetts, November 2015.
\mytalkurl{Northeastern15-Scal-Scalloc-Selfie}.

\item \emph{Distributed Queues: Faster Pools and Better Queues},
Oracle, Belmont, California, December 2012.
\mytalkurl{Oracle12-DQ}.

\item \emph{Distributed Queues: Faster Pools and Better Queues},
Stanford University, Palo Alto, California, December 2012.
\mytalkurl{Stanford12-DQ}.

\item \emph{Incorrect Systems: It's not the Problem, It's the Solution},
DREAMS Seminar, UC Berkeley, Berkeley, California, July 2012.
\mytalkurl{UCB12-Incorrectness}.

\item \emph{The Next Frontier of Cloud Computing is in the Clouds, Literally}, AI-Systems-Robotics Seminar, CS Department, Cornell University, Ithaca, New York, February 2011.
\mytalkurl{Cornell11-CPCC}.

\item \emph{The Next Frontier of Cloud Computing is in the Clouds, Literally}, CS Department, UC Davis, Davis, California, February 2011.
\mytalkurl{UCD11-CPCC}.

\item \emph{Scal$\skull$: Non-Linearizable Computing Breaks the Scalability Barrier},
Center for Hybrid and Embedded Software Systems, UC Berkeley, Berkeley, California, November 2010.
\mytalkurl{UCB10-Scal}.

\item \emph{Short-term Memory for Self-collecting Mutators},
Center for Hybrid and Embedded Software Systems, UC Berkeley, Berkeley, California, September 2010.
\mytalkurl{UCB10-STM}.

\item \emph{The Next Frontier of Cloud Computing is in the Clouds, Literally}, Google Tech Talk, Mountain View, California, September 2010.
\mytalkurl{Google10-CPCC}.

\item \emph{Short-term Memory for Self-collecting Mutators}, CSAIL, MIT, Boston, Massachusetts, May 2010.
\mytalkurl{MIT10-STM}.

\item \emph{Distributed, Modular HTL},
Department of Electrical Engineering and Information Technology, Technical University of Munich, Munich, Germany, June 2009.
\mytalkurl{TUM09-Modular-HTL}.

\item \emph{Time-Portable Programming the JAviator in the Tiptoe VM},
Center for Hybrid and Embedded Software Systems, UC Berkeley, Berkeley, California, January 2009.
\mytalkurl{UCB09-JAviator}.

\item \emph{The JAviator: Time-Portable Programming in Java and C},
Hitachi Global Storage Technologies, San Jose, California, September 2008.
\mytalkurl{Hitachi08-JAviator}.

\item \emph{The JAviator: Time-Portable Programming in Java},
Sun Microsystems, Palo Alto, California, September 2008.
\mytalkurl{Sun08-JAviator}.

\item \emph{Tiptoe: A Compositional Real-Time Operating System (Process Model and Scheduler)},
EPFL, Lausanne, Switzerland, May 2008.
\mytalkurl{EPFL08-Tiptoe}.

\item \emph{Tiptoe: A Compositional Real-Time Operating System (Process Model and Scheduler)},
ETHZ, Z{\"u}rich, Switzerland, May 2008.
\mytalkurl{ETHZ08-Tiptoe}.

\item \emph{Tiptoe: A Compositional Real-Time Operating System (Memory Management)},
IBM T.J. Watson Research Center, Hawthorne, New York, September 2007.
\mytalkurl{IBM07-Tiptoe}.

\item \emph{Time-Portable Real-Time Programming with Exotasks},
Center for Hybrid and Embedded Software Systems, UC Berkeley, Berkeley, California, February 2007.
\mytalkurl{UCB07-Exotasks}.

\item \emph{An Introduction to Logical Execution Time Programming},
Center for Collaborative Control of Unmanned Vehicles, UC Berkeley, Berkeley, California, September 2006.
\mytalkurl{UCB06-IntroductionLET}.

\item \emph{High-Level Programming of Real-Time Software Systems},
University of Lugano, Lugano, Switzerland, March 2006.
\mytalkurl{Lugano06-HighLevelProgramming}.

\item \emph{The JAviator Project},
Center for Hybrid and Embedded Software Systems, UC Berkeley, Berkeley, California, February 2006.
\mytalkurl{UCB06-JAviator}.

\item \emph{High-Level Programming of Real-Time and Concurrent Software Systems},
Purdue University, West Lafayette, Indiana, December 2005.
\mytalkurl{Purdue05-HighLevelProgramming}.

\item \emph{Traffic Shaping System Calls Using Threading by Appointment},
UC Berkeley, Berkeley, California, September 2005.
\mytalkurl{UCB05-TrafficShapingSystemCallsTAP}.

\item \emph{Traffic Shaping System Calls Using Threading by Appointment},
UCLA, Los Angeles, California, August 2005.
\mytalkurl{UCLA05-TrafficShapingSystemCallsTAP}.

\item \emph{The Embedded Machine: Status and Future Directions},
IBM T.J. Watson Research Center, Hawthorne, New York, March 2005.
\mytalkurl{IBM05-EmbeddedMachine}.

\item \emph{Threading by Appointment},
Center for Collaborative Control of Unmanned Vehicles, UC Berkeley, Berkeley, California, February 2005.
\mytalkurl{UCB05-TAP}.

\item \emph{Real-Time Programming Based on Schedule-Carrying Code},
McGill University, Montreal, Canada, January, 2004.
\mytalkurl{McGill04-RTProgrammingSCC}.

\item \emph{The Embedded Machine: Predictable, Portable Real-Time Code},
Verimag, Grenoble, France, November 2001.
\mytalkurl{Verimag01-EmbeddedMachine}.

\item \emph{Giotto: A Time-triggered Language for Embedded Programming},
Honeywell, Minneapolis, Minnesota, September 2001.
\mytalkurl{Honeywell01-Giotto}.

\item \emph{Embedded Control Systems Development with Giotto},
Stanford University, Palo Alto, California, November 2000.
\mytalkurl{Stanford00-Giotto}.
\end{enumerate}
}